Testing traversability of protein tunnels with flexible ligands using motion planning

### 2017-06-14 paper.tex
Added figures of tunnel properties

\red{Adam: }
As described above, our approach enables to estimate the probability that a ligand given a minimum scale passes through a tunnel.
On the other hand, the probability does not describe any details about the ligand's passage, e.g., how hard it is to pass some part of the tunnel, which trajectory is the most used, etc.
Moreover, it is not feasible to directly visualize and explore the resulting trajectories due to the visual clutter (see Fig.~\ref{fig:trajectories} left) caused by their high number and close proximity.
Therefore, we propose to extract and visualize the complex information about the ligand's passage through a tunnel.
In this manner, we aim to further support the decision process of a chemist about a tunnel.
In order to do that, we employ an ensemble of resulting trajectories, and we compute and visualize the following tunnel properties:
\begin{itemize}
  \item \textbf{Accessibility} --- The probability of the ligand that it reaches a tunnel's part.
  \red{ i.e., number of trajectories ending in the tunnel part over all trajectories? }
  \item \textbf{Ligand Scale} --- The scale of the ligand wheh it passes a tunnel's part.
  \item \textbf{Throughput} --- The probability of the ligand that it passes through a tunnel's part.
\red{ i.e., the conditional probability we discussed in the mail?}
\end{itemize}
During visualization, we map these properties onto a tunnel's surface so that they can be visually correlated with, e.g., the tunnel's shape.

@@

\begin{figure}
\centering
\begin{tabular}{cccccc}
\includegraphics[width=0.45\textwidth]{fig/trajectories-all}
\qquad & \qquad
\includegraphics[width=0.45\textwidth]{fig/trajectories-clustered-21} \\
\end{tabular}
\caption{Visualization of resulting trajectories.
Left: All trajectories colored according to whether they reached the end of the tunnel (green) or they did not (red).
Right: Trajectories clustered according to their proximity colored by distinct colors.
The different line widths represent the number of trajectories in a cluster.}
\label{fig:trajectories}
\end{figure}

>>>>

\red{Adam: }
As described above, our approach enables to estimate the probability that a ligand given a minimum scale passes through a tunnel.
On the other hand, the probability does not describe any details about the ligand's passage, e.g., how hard it is to pass some part of the tunnel, which trajectory is the most used, etc.
Moreover, it is not feasible to directly visualize and explore the resulting trajectories due to the visual clutter (see Fig.~\ref{fig:trajectories} left) caused by their high number and close proximity.
Therefore, we propose to extract and visualize the complex information about the ligand's passage through a tunnel.
In this manner, we aim to further support the decision process of a chemist about a tunnel.
In order to do that, we employ an ensemble of resulting trajectories, and we compute and visualize the following tunnel properties:
\begin{itemize}
  \item \textbf{Accessibility} --- The probability of the ligand that it reaches a tunnel's part.
  \red{ i.e., number of trajectories ending in the tunnel part over all trajectories? }
  \item \textbf{Ligand scale} --- The scale of the ligand wheh it passes a tunnel's part.
  \item \textbf{Throughput} --- The probability of the ligand that it passes through a tunnel's part.
\red{ i.e., the conditional probability we discussed in the mail?}
\end{itemize}
During visualization, we map these properties onto a tunnel's surface (see Fig.~\ref{fig:properties}) so that they can be visually correlated with, e.g., the tunnel's shape.

\begin{figure}
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\textwidth]{fig/accessibility}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/ligand-scale}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/throughput}
\end{tabular}
\caption{Tunnel properties mapped onto its surface.
Left: Accessibility --- green denotes parts that were accesed by the ligand easily while red denotes parts that were accessible only in about 10\% of computations.
Middle: Ligand scale --- the average scale of the ligand was \~50\% in orange parts, \~60\% in yellow parts, \~80\% in yellow to green parts and \~100\% in green parts.
Right: Throughput --- green denotes parts that are highly probable to be passed by the ligand while red denotes those that were hard to pass.}
\label{fig:properties}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{fig/trajectories-all}
\qquad & \qquad
\includegraphics[width=0.45\textwidth]{fig/trajectories-clustered-21} \\
\end{tabular}
\caption{Visualization of resulting trajectories.
Left: All trajectories colored according to whether they reached the end of the tunnel (green) or they did not (red).
Right: Trajectories clustered according to their proximity colored by distinct colors.
The different line widths represent the number of trajectories in a cluster.}
\label{fig:trajectories}
\end{figure}
